\section*{\hfill Request for Contributions \hfill}

The NIST Big Data Public Working Group (NBD-PWG) requests
contributions to this draft Version 2 of the NIST Big Data
Interoperability Framework (NBDIF): Volume 6, Reference Architecture.
All contributions are welcome, especially comments or additional
content for the current draft. 

The NBD-PWG is actively working to complete Version 2 of the set of NBDIF documents. The goals of Version 2 are to enhance the Version 1 content, define general interfaces between the NIST Big Data Reference Architecture (NBDRA) components by aggregating low-level interactions into high-level general interfaces, and demonstrate how the NBDRA can be used. 
To contribute to this document, please follow the steps below as soon as possible but no later than September 21, 2017.

\begin{enumerate}

\item	Obtain your user ID by registering as a user of the NBD-PWG
  Portal (\url{https://bigdatawg.nist.gov/newuser.php})

\item	Record comments and/or additional content in one of the
  following methods:

  \begin{enumerate}

  \item {\bf\underline{TRACK CHANGES}:} make edits to and comments on the text
    directly into this Word document using track changes

    \item {\bf\underline{COMMENT TEMPLATE}:} capture specific edits using the Comment
      Template
      (\url{http://bigdatawg.nist.gov/_uploadfiles/SP1500-1-to-7_comment_template.docx}),
      which includes space for section number, page number, comment,
      and text edits

\end{enumerate}

\item Submit the edited file from either method above by uploading the
  document to the NBD-PWG portal
  (\url{https://bigdatawg.nist.gov/upload.php}). Use the User ID
  (obtained in step 1) to upload documents. Alternatively, the edited
  file (from step 2) can be emailed to SP1500comments@nist.gov with
  the volume number in the subject line (e.g., Edits for Volume 1).

\item	Attend the weekly virtual meetings on Tuesdays for possible
  presentation and discussion of your submission. Virtual meeting
  logistics can be found at
  \url{https://bigdatawg.nist.gov/program.php}
\end{enumerate}

Please be as specific as possible in any comments or edits to the text. Specific edits include, but are not limited to, changes in the current text, additional text further explaining a topic or explaining a new topic, additional references, or comments about the text, topics, or document organization. 

The comments and additional content will be reviewed by the subgroup co-chair responsible for the volume in question. Comments and additional content may be presented and discussed by the NBD-PWG during the weekly virtual meetings on Tuesday. 

Three versions are planned for the NBDIF set of documents, with Versions 2 and 3 building on the first. Further explanation of the three planned versions, and the information contained therein, is included in Section 1 of each NBDIF document.

Please contact Wo Chang (wchang@nist.gov) with any questions about the feedback submission process. 

Big Data professionals are always welcome to join the NBD-PWG to help craft the work contained in the volumes of the NBDIF. Additional information about the NBD-PWG can be found at \url{http://bigdatawg.nist.gov}. Information about the weekly virtual meetings on Tuesday can be found at \url{https://bigdatawg.nist.gov/program.php}. 

